The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-12 methods/ms.tex
distmaps continued, minor ms.tex correction

The resulting map is then subjected to a Hogbom-type CLEAN algorithm
\citep{hogbom} using a specified kernel to produce a deconvolved image
which is the one actually mapped back into the timestream to be
subtracted (Equation \ref{eq:MapToTime}.  This has several advantages
over using the original map directly, including rejecting artefacts
smaller than the beam and decreasing the noise of the resulting
timestream.  It is also better than a ``threshold'' method, which
tends to produce discontinuities.

>>>>

The resulting map is then subjected to a maximum-entropy CLEAN algorithm
%\citep{hogbom} 
using a specified kernel to produce a deconvolved image
which is the one actually mapped back into the timestream to be
subtracted (Equation \ref{eq:MapToTime}.  This has several advantages
over using the original map directly, including rejecting artefacts
smaller than the beam and decreasing the noise of the resulting
timestream.  It is also better than a ``threshold'' method, which
tends to produce discontinuities.
